Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Tune tables

    Respective event counts are given for the whole stimulus (\texttt{all} and

@@

\begin{tabular}{lp{3.7cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\

@@

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[tbp]
    \caption{Categories and rules to categorize the nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as basis to build the regressors of the
        GLM
        (Tab.~\ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lp{61mm}p{61mm}}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
\texttt{bodypart} & limbs & arm, finger, leg, toe
\tabularnewline
\texttt{face} & face or parts of it & face, ear, nose, mouth
\tabularnewline
\texttt{female} & female person & nurse, mother, woman
\tabularnewline
\texttt{females} & female persons & women
\tabularnewline
\texttt{fname} & female name & Jenny
\tabularnewline
\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
\tabularnewline
\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
\tabularnewline
\texttt{groom} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
helmet
\tabularnewline
\texttt{male} & male person & man, father, soldier
\tabularnewline
\texttt{males} & male persons & boys, opponents
\tabularnewline
\texttt{mname} & male name & Bubba, Kennedy
\tabularnewline
\texttt{object} & countable entity with firm boundaries & telephone, car
\tabularnewline
\texttt{objects} & countable entities & wheels, plants
\tabularnewline
\texttt{persons} & concrete persons of unknown sex & hippies, patients
\tabularnewline
\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\

@@

% intro
We performed standard two-level GLM analyses to aggregate results across the 8
segments for every participant and each stimulus separately.
% level 3
Subsequently, we conducted third-level analyses to average contrast estimates
over participants for each stimulus, respectively.

@@

\begin{table*}[tbp]
\caption{Computed contrasts for the analysis of the movie and their purpose.}
\label{tab:av-contrasts}
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & \texttt{vse\_new > vpe\_old} & spatial processing \tabularnewline
2 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
3 & \texttt{vse\_new > vse\_old} & spatial processing \tabularnewline
4 & \texttt{vse\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
5 & \texttt{vse\_new, vpe\_new > vpe\_old} & spatial processing \tabularnewline
6 & \texttt{vno\_cut > vse\_new} & control \tabularnewline
7 & \texttt{vno\_cut > vse\_old} & control \tabularnewline
8 & \texttt{vno\_cut > vse\_new, vse\_old} & control \tabularnewline
9 & \texttt{vno\_cut > vpe\_new, vpe\_old} & control \tabularnewline
10 & \texttt{se\_new > se\_old} & control for (missing) narrator \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[tbp]
\caption{Computed contrasts for the analysis of the audio-description and their purpose.
    \texttt{non-spatial} refers to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.}
\label{tab:ao-contrasts}
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & \texttt{geo, groom > non-spatial} & spatial processing \tabularnewline
2 & \texttt{geo, groom, se\_new > non-spatial} & spatial processing \tabularnewline
3 & \texttt{groom, se\_new, se\_old > non-spatial}  & spatial processing \tabularnewline
4 & \texttt{geo > non-spatial} & spatial processing \tabularnewline
5 & \texttt{groom > non-spatial} & spatial processing \tabularnewline
6 & \texttt{se\_new > non-spatial} & spatial processing \tabularnewline
7 & \texttt{se\_new, se\_old > non-spatial} & spatial processing \tabularnewline
8 & \texttt{se\_new > se\_old > non-spatial} & spatial processing \tabularnewline
9 & \texttt{vse\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
10 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
11 & \texttt{vse\_new > vse\_old} & control (absent visual cuts) \tabularnewline
12 & \texttt{vse\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
13 & \texttt{vse\_new, vpe\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\begin{table*}[tbp]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting depicted for the first time with cuts within a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & <.00001 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
154 & <.00001 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior
lateral occipital c. \\ % 0.000000656
121 & <.00001 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior
lateral occipital cortex \\ % 0.00000769
\bottomrule
\end{tabular}
\end{table*}

% table group results primary AD contrast
\begin{table*}[tbp]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & <.00001 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l.
precuneus \\ % 0.0000000596
164 & <.00001 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus;
\\ % 0.000000238
83 & .00013 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal
(occipital) fusiform c.; posterior parahippocampal g. \\ % 0.000128
73 & .00031 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual
g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\ % 0.000128
63 & .00082 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior
lateral occipital c. \\ % 0.000824
37 & .0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior
lateral occipital c. \\ % 0.0129
\bottomrule
\end{tabular}
\end{table*}

>>>>

    Respective event counts are given for the whole stimulus (\texttt{All} and

@@

\begin{tabular}{lp{3.7cm}lllllllll} \toprule \textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\

@@

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[tbp]
    \caption{Categories and rules to categorize the nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as basis to build the regressors of the
        GLM
        (Tab.~\ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lp{61mm}p{61mm}}
\toprule
\textbf{Category} & \textbf{Rule} & \textbf{Examples} \\
\midrule
\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
\texttt{bodypart} & limbs & arm, finger, leg, toe
\tabularnewline
\texttt{face} & face or parts of it & face, ear, nose, mouth
\tabularnewline
\texttt{female} & female person & nurse, mother, woman
\tabularnewline
\texttt{females} & female persons & women
\tabularnewline
\texttt{fname} & female name & Jenny
\tabularnewline
\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
\tabularnewline
\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
\tabularnewline
\texttt{groom} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
helmet
\tabularnewline
\texttt{male} & male person & man, father, soldier
\tabularnewline
\texttt{males} & male persons & boys, opponents
\tabularnewline
\texttt{mname} & male name & Bubba, Kennedy
\tabularnewline
\texttt{object} & countable entity with firm boundaries & telephone, car
\tabularnewline
\texttt{objects} & countable entities & wheels, plants
\tabularnewline
\texttt{persons} & concrete persons of unknown sex & hippies, patients
\tabularnewline
\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\toprule \textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\

@@

% intro
We performed standard two-level GLM analyses to aggregate results across the eight
segments for every participant and each stimulus separately.
% level 3
Subsequently, we conducted third-level analyses to average contrast estimates
over participants for each stimulus, respectively.

@@

\begin{table*}[tbp]
\caption{Computed contrasts for the analysis of the movie and their purpose.}
\label{tab:av-contrasts}
\begin{tabular}{lll}
\toprule
\textbf{Nr.} &  \textbf{Contrast} & \textbf{Purpose} \\
\midrule
1 & \texttt{vse\_new > vpe\_old} & spatial processing \tabularnewline
2 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
3 & \texttt{vse\_new > vse\_old} & spatial processing \tabularnewline
4 & \texttt{vse\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
5 & \texttt{vse\_new, vpe\_new > vpe\_old} & spatial processing \tabularnewline
6 & \texttt{vno\_cut > vse\_new} & control \tabularnewline
7 & \texttt{vno\_cut > vse\_old} & control \tabularnewline
8 & \texttt{vno\_cut > vse\_new, vse\_old} & control \tabularnewline
9 & \texttt{vno\_cut > vpe\_new, vpe\_old} & control \tabularnewline
10 & \texttt{se\_new > se\_old} & control for (missing) narrator \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[tbp]
\caption{Computed contrasts for the analysis of the audio-description and their purpose.
    \texttt{non-spatial} refers to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.}
\label{tab:ao-contrasts}
\begin{tabular}{lll}
\toprule
\textbf{Nr.} &  \textbf{Contrast} & \textbf{Purpose} \\
\midrule
1 & \texttt{geo, groom > non-spatial} & spatial processing \tabularnewline
2 & \texttt{geo, groom, se\_new > non-spatial} & spatial processing \tabularnewline
3 & \texttt{groom, se\_new, se\_old > non-spatial}  & spatial processing \tabularnewline
4 & \texttt{geo > non-spatial} & spatial processing \tabularnewline
5 & \texttt{groom > non-spatial} & spatial processing \tabularnewline
6 & \texttt{se\_new > non-spatial} & spatial processing \tabularnewline
7 & \texttt{se\_new, se\_old > non-spatial} & spatial processing \tabularnewline
8 & \texttt{se\_new > se\_old > non-spatial} & spatial processing \tabularnewline
9 & \texttt{vse\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
10 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
11 & \texttt{vse\_new > vse\_old} & control (absent visual cuts) \tabularnewline
12 & \texttt{vse\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
13 & \texttt{vse\_new, vpe\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\begin{table*}[tbp]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting depicted for the first time with cuts within a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).
    CoG: Center of Gravity}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3.5cm}}
\toprule
& & & \multicolumn{3}{r}{Max (MNI)} & \multicolumn{3}{r}{CoG (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
Voxels & $p_{corr.}$ & Z-max & X & Y & Z  & X & Y & Z & Structure \\
\midrule
3003 & <.00001 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
154 & <.00001 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior
lateral occipital c. \\ % 0.000000656
121 & <.00001 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior
lateral occipital cortex \\ % 0.00000769
\bottomrule
\end{tabular}
\end{table*}

% table group results primary AD contrast
\begin{table*}[tbp]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).
    CoG: Center of Gravity}
    \label{tab:res-ao-group1}
    \begin{tabular}{rrrrrrrrrp{3.5cm}}
\toprule
& & & \multicolumn{3}{r}{Max (MNI)} & \multicolumn{3}{r}{CoG (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
Voxels & $p_{corr.}$ & Z-max & X & Y & Z  & X & Y & Z & Structure \\
\midrule
188 & <.00001 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l.
precuneus \\ % 0.0000000596
164 & <.00001 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus;
\\ % 0.000000238
83 & .00013 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal
(occipital) fusiform c.; posterior parahippocampal g. \\ % 0.000128
73 & .00031 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual
g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\ % 0.000128
63 & .00082 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior
lateral occipital c. \\ % 0.000824
37 & .0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior
lateral occipital c. \\ % 0.0129
\bottomrule
\end{tabular}
\end{table*}
